Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-01-28 paper/main.tex
Updates

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
% \usepackage[ruled]{algorithm2e}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\textwidth}
		\caption{\todo[inline]{Add the prompt used}}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[scale=0.3]{../code/fig5/llm_adult.png}
		\caption{\todo[inline]{Change figure to have consistent style}}
	\end{subfigure}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{fancyvrb}
% \usepackage[ruled]{algorithm2e}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\textwidth}
		\begin{Verbatim}[fontsize=\footnotesize]
You are an expert in Social Science. Following
are the descriptions of two variables:

<A>: {description of variable A}
<B>: {description of variable B}

Which of the following two options is the most 
likely causal direction between these variables:

1. <A> causes <B>
2. <B> causes <A>

Return a single letter answer between the 
choices above; Do not provide any reasoning 
in the answer; Do not add any text formatting 
to the answer.
		\end{Verbatim}
	\caption{Prompt used for the LLM}
	\end{subfigure}
	\begin{subfigure}{0.5 \textwidth}
		\begin{Verbatim}[fontsize=\footnotesize]
Age: The age of a person
Workclass: The workplace where the person is 
     employed such as Private industry, 
     or self employed
Education: The highest level of education the 
     person has finished
MaritalStatus: The marital status of the person
Occupation: The kind of job the person does. 
     For example, sales, craft repair, clerical.
Relationship: The relationship status of 
     the person
Race: The ethnicity of the person
Sex: The sex or gender of the person
HoursPerWeek: The number of hours per week the 
     person works
NativeCountry: The native country of the person
Income: The income i.e. amount of money the 
     person makes
		\end{Verbatim}
	\caption{Variable descriptions used for prompting the LLM}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[scale=0.3]{../code/fig5/llm_adult.png}
		\caption{The learned DAG}
	\end{subfigure}
\end{figure}
